Data preparation - JOAs

### 2023-03-15 04. Analysis/scripts/01-data-preparation-joas.Rmd
Update 01-data-preparation-joas.Rmd
example from opm work updated

---
title: "Data preparation - JOAs"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: readable
    highlight: tango
    code_folding: hide
params:
  author: "Sam Kim and Ben Jaques-Leslie"
  project_number: "001"
  project_name: "Remote Work"
  data_folder_1: "03. Data Collection/Original data files from Melissa/JOAs"
  unique_identifier_1: !r c("usajobs_control_number")
  date_earliest_open: '2022-01-01'
  data_latest_close: '2022-12-01'
---

@@

if(!("announcement_closing_type" %in% names(prep_03)) &
   !("agency_level" %in% names(prep_03)) &
   !("hiring_department_code" %in% names(prep_03)) &
   !("hiring_agency_code" %in% names(prep_03)) 
     )
{
  prep_04 <-
  prep_03 %>%
  mutate(
    across(
      .cols = c(position_open_date,position_close_date),
      .fns = ~ymd(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(usajobs_control_number,
                # announcement_closing_type,
                # agency_level,
                # hiring_department_code,
                series),
      .fns = ~as.character(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(
        # hiring_agency_code,
        total_openings),
      .fns = ~str_trim(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(total_openings),
      .fns = ~as.numeric(.)
    )
  )
}

@@

```{r}
files_full <- 
  files %>% 
  filter(str_detect(file,"_full_") | str_detect(file,"Positions_Updated_Dec2022")) %>%
  select(file,encoding)

@@

@@

```{r}
prep_base <- 
  map2_dfr(
    .x = files_full$file,
    .y = files_full$encoding,
    .f = ~load_prepare_joa(in_file_name = .x, in_encoding = .y)
  ) %>% 
  distinct()
```

@@

@@

@@

```{r}
duplicating_variables <- 
  duplicating_variables %>% 
  mutate(group = 
           case_when(variable == "position_open_date" ~ "dates",
                     variable == "position_close_date" ~ "dates",
                     variable == "announcement_closing_type" ~ "announcement_closing_type",
                     variable == "announcement_closing_type_description" ~ "announcement_closing_type",
                     variable == "application_limit" ~ "application_limit",
                     variable == "application_limit_set" ~ "application_limit",
                     variable == "agency_level" ~ "agency_level",
                     variable == "agency_level_sort" ~ "agency_level",
                     variable == "hiring_agency_code" ~ "agency_level",
                     variable == "hiring_agency_name" ~ "agency_level",
                     variable == "hiring_department_code" ~ "agency_level",
                     variable == "hiring_department_name" ~ "agency_level",
                     variable == "maximum_salary" ~ "maximum_salary",
                     variable == "minimum_salary" ~ "maximum_salary",
                     variable == "maximum_grade" ~ "maximum_salary",
                     variable == "minimum_grade" ~ "maximum_salary",
                     variable == "series" ~ "series",
                     variable == "series_title" ~ "series",
                     TRUE ~ variable
                     ))

@@

```{r}
duplicating_groups <- 
  duplicating_variables %>% 
  select(group) %>% 
  distinct() %>% 
  pull()

@@

@@

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  mutate(
    announcement_number = str_to_upper(announcement_number)
  ) %>% 
  distinct() %>% 
  arrange(params$unique_identifier_1,announcement_number) %>% 
  group_by_at(params$unique_identifier_1) %>% 
  summarise(announcement_number = first(announcement_number))

@@

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

@@

@@

@@

Duplication appear to be because of difference in open and close dates. After messaging with Melissa, we decide to retain the later dates as determined by the close date.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

@@

```{r}
prep_02 <- prep_xx
```

@@

@@

@@

```{r}
prep_xx <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  mutate(
    is_remote_work_eligible = case_when(is_remote_work_eligible == "" ~ "N",
                                        TRUE ~ is_remote_work_eligible)
  ) %>% 
  distinct() %>% 
  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
                         in_variable = is_remote_work_eligible,
                         in_prefix = "is_remote_work_eligible") %>% 
  # Drop the "n" indicatoris_remote_work_eligible
  select(-is_remote_work_eligible_n)

@@

```{r}
prep_03 <- prep_xx
```

@@

@@

@@

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,announcement_closing_type_description,"closing_type")

```{r}
prep_04 <- prep_xx

Announcements have multiple open statuses.

```{r}
prep_base %>% count(position_opening_status)
```

Not too many of them. Like above, we will transform these into indicator columns.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,position_opening_status,"position_opening_status")

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```
Rename dataframe

```{r}
prep_05 <- prep_xx

Not too many. It appears that `application_limit_set` is "N" when `application_limit` is "Applicant Cut-Off".

All NA `application_limit` are "N" `application_limit_set`.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,application_limit_set,"application_limit_set") %>% 
  # Drop the "N" column
  select(-application_limit_set_n)

@@

```{r}
prep_06 <- prep_xx
```

@@

@@

Not too many. It appears that `work_schedule` might have different.

@@

```{r}
prep_base %>% count(work_schedule)
```

@@

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,work_schedule,"work_schedule")

@@

```{r}
prep_07 <- prep_xx
```

@@

Not too many. It appears that `disable_apply_online` might have different.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,disable_apply_online,"disable_apply_online") %>% 
  # Drop the "N" column
  select(-disable_apply_online_n)

```{r}
prep_08 <- prep_xx
```

Not too many.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,appointment_type,"appointment_type")

```{r}
prep_09 <- prep_xx
```

1.    Department of Defense agencies are duplicated because sometimes sub-departments (e.i. Department of Navy) are considered the *Department*
2.    Many duplicates are caused by blank values in hiring agency code

First let's remove duplicates because of department. To do this, we'll use the maximum agency level to limit to just the entries with the most levels.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  group_by(usajobs_control_number) %>% 
  filter(agency_level == max(agency_level)) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

We can still see the duplications from blank hiring agency codes. We'll drop those.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  group_by(usajobs_control_number) %>% 
  filter(agency_level == max(agency_level)) %>% 
  filter(!is.na(hiring_department_code)) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

We still have one duplicate remaining. For this we'll, select the entry with the later position closing date.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  filter(agency_level == max(agency_level)) %>% 
  filter(!is.na(hiring_department_code)) %>% 
  filter(position_close_date == max(position_close_date)) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

Now we will apply all of these to the duplicated rows.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  filter(agency_level == max(agency_level)) %>% 
  filter(!is.na(hiring_department_code)) %>% 
  filter(position_close_date == max(position_close_date)) %>% 
  distinct() %>% 
  ungroup() %>% 
  select(-position_close_date)

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

```{r}
prep_10 <- prep_xx
```

@@

@@

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

@@

```{r}
prep_11 <- prep_xx
```

@@

@@

dupe_02
```
Count types.

```{r}
prep_base %>% 
  count(series, series_title)
```

Many different titles and series.

Check if the series numbers are duplicated.

```{r}
prep_base %>% 
  count(series, series_title) %>% 
  ungroup() %>% 
  get_dupes(series)
```

None.

Now the titles.

```{r}
prep_base %>% 
  count(series, series_title) %>% 
  ungroup() %>% 
  get_dupes(series_title)
```

None.

Since the `series` adds no information and is uniquely matched to the titles, we will drop `series`.

There are too many series to want indicators, we'll use the last closing date to select the appropriate series.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe) %>% 
  select(-series)

@@

@@

Not too many duplicates. We'll follow the same procedure, taking the number from the row wiht the later closing date.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

>>>>

---
title: "Data preparation - JOAs"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: readable
    highlight: tango
    code_folding: hide
params:
  author: "Sam Kim and Ben Jaques-Leslie"
  project_number: "001"
  project_name: "Remote Work"
  data_folder_1: "03. Data Collection/Original data files from Melissa/JOAs"
  unique_identifier_1: !r c("usajobs_control_number")
  date_earliest_open: '2022-01-01'
  data_latest_close: '2022-12-31'
---

@@

if(!("announcement_closing_type" %in% names(prep_03)) &
   !("agency_level" %in% names(prep_03)) &
   !("hiring_department_code" %in% names(prep_03)) &
   !("hiring_agency_code" %in% names(prep_03)) 
     )
{
  prep_04 <-
  prep_03 %>%
  mutate(
    across(
      .cols = c(position_open_date,position_close_date),
      .fns = ~ymd(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = starts_with("usajobs_control_number")|
                # announcement_closing_type,
                # agency_level,
                # hiring_department_code,
                starts_with("series"),
      .fns = ~as.character(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(
        # hiring_agency_code,
        total_openings),
      .fns = ~str_trim(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(total_openings),
      .fns = ~as.numeric(.)
    )
  )
}

@@

```{r}
files_full <- 
  files %>% 
  filter(str_detect(file,"_full_") | 
           str_detect(file,"Positions_Updated_Dec2022") 
         ) %>%
  select(file,encoding)

@@

#### Load 'allpositionsopenedduring2022'

Load position headers for the data.

```{r}
positions_headers <- 
  here::here(params$data_folder_1,"positions_headers.csv") %>% 
  read_csv() %>% 
      distinct()
```

Load the data and apply the position headers.

```{r}
prep_all_positions <- 
  files %>% 
  filter(
    str_detect(file,"allpositionsopenedduring2022")
         ) %>%
  pull(file) %>%  
  load_utf8(
  ) %>% 
  rename_all(~names(positions_headers)) %>% 
  clean_names() %>% 
  prepare_joa()
```

@@

```{r}
prep_base <- 
  map2_dfr(
    .x = files_full$file,
    .y = files_full$encoding,
    .f = ~load_prepare_joa(in_file_name = .x, in_encoding = .y)
  ) %>% 
  bind_rows(prep_all_positions) %>% 
  distinct()
```

@@

#### Load 'hiring path' files

Load first hiring path file.

```{r}
prep_hiring_path_01 <- 
   read_csv(here::here(params$data_folder_1,"hiringpath_remotework.csv"),
   col_types = cols(`Hiring Path` = col_character(), 
        `Position Open Date` = col_skip(), 
        `Position Close Date` = col_skip(), 
        `USAJOBS Control Number` = col_character())
   ) %>% 
  clean_names() %>% 
  distinct()
```

Collect the names from the dataframe.

```{r}
prep_hiring_path_01_names <- sort(names(prep_hiring_path_01), decreasing = TRUE)
```

Load second hiring path file, and apply names from the first dataset.

```{r}
prep_hiring_path_02 <- read_csv(here::here(params$data_folder_1,"positions - hiring path - 2022.csv"),
    col_names = FALSE, col_types = cols(X1 = col_character(), 
        X2 = col_skip(), X3 = col_skip(), 
        X4 = col_character())) %>% 
  distinct() %>% 
  rename_at(
    vars(everything()),
    ~prep_hiring_path_01_names
  )
```

Bind dataframes and convert hiring path to indicators.

```{r}
prep_hiring_path <- 
  prep_hiring_path_01 %>% 
  bind_rows(prep_hiring_path_02) %>% 
  distinct() %>% 
  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
                         in_variable = hiring_path,
                         in_prefix = "hiring_path")

```{r}
prep_hiring_path %>% 
  skim()
```

#### Load 'work schedule and appointment type' files

Load first work schedule and appointment type file.

```{r}
prep_work_schedule_appointment_01 <- 
   read_csv(here::here(params$data_folder_1,"positions - work schedule and appointment type.csv"), 
    col_types = cols(Announcement_Number = col_skip(), 
        USAJOBS_Control_Number = col_character())
   ) %>% 
  clean_names() %>% 
  distinct()
```

Convert work schedule to indicators.

```{r}
prep_work_schedule <- 
  prep_work_schedule_appointment_01 %>% 
  distinct() %>% 
  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
                         in_variable = position_work_schedule_type,
                         in_prefix = "work_schedule")

Convert appointment type to indicators.

```{r}
prep_appointment <- 
  prep_work_schedule_appointment_01 %>% 
  distinct() %>% 
  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
                         in_variable = position_appointment_type,
                         in_prefix = "appointment_type")

Join indicator dataframes.

```{r}
prep_work_schedule_appointment <- 
  prep_work_schedule %>% 
  full_join(prep_appointment)
```

```{r}
prep_work_schedule_appointment %>% 
  skim()
```

#### Load 'series' files

Load first series file.

```{r}
prep_series_01 <- 
   read_csv(here::here(params$data_folder_1,"positions - series - 2022.csv"), 
    col_types = cols(USAJOBS_Control_Number = col_character(), 
        Announcement_Number = col_skip(), 
        Series = col_character(), Series_Title = col_character())) %>% 
  clean_names() %>% 
  distinct()
```

Rename.

```{r}
prep_series <- 
  prep_series_01
```

```{r}
prep_series %>% 
  skim()
```

#### Load 'locations' files

Load first locations file.

```{r}
prep_locations_01 <- 
   read_csv(here::here(params$data_folder_1,"positions - locations - 2022.csv"), 
   col_types = cols(`Announcement Number` = col_skip(), 
        `USAJOBS Control Number` = col_character(), 
        `Position Open Date` = col_date(format = "%m/%d/%Y"), 
        `Position Close Date` = col_date(format = "%m/%d/%Y"), 
        `Position Location City` = col_character(), 
        `Position Location Country` = col_character(), 
        `Position Location Geo-location Code` = col_character(), 
        `Position Location State` = col_character(), 
        `Position Location Zip` = col_character())) %>% 
  clean_names() %>% 
  distinct()
```

Rename.

```{r}
prep_location <- 
  prep_locations_01
```

```{r}
prep_location %>% 
  skim()
```

Check for duplicates.

```{r}
dupes_location <- 
  prep_location %>% 
  get_dupes(params$unique_identifier_1)

dupes_location
```

Count by number of duplications.

```{r}
dupes_location %>% 
  count(dupe_count)
```
Count number of `position_location_geo_location_code`.

```{r}
location_count <- 
  prep_location %>% 
  group_by(position_location_city,position_location_country,
           position_location_geo_location_code,
           position_location_state,position_location_zip) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rownames_to_column(var = 'rank')

location_count
```

Check to see if any of these 'NULL' are duplicated.

```{r}
dupes_location %>% 
  filter(position_location_geo_location_code == "NULL")
```

Aggregate location data to deduplicate, counting multiple locations.

```{r}
prep_location_n_distinct <- 
  prep_location %>%
  group_by(usajobs_control_number
           ,position_close_date, 
           position_open_date
           ) %>%
  summarise(
    across(
      .cols = everything(),
      .fns = ~n_distinct(.),
      .names = "{.col}_n_distinct"
      )
  ) %>% 
  ungroup() %>% 
  mutate(
    multiple_location_ind = 
      case_when(if_any(ends_with("_n_distinct"), ~ .x > 1) ~ 1,
                TRUE ~ 0
                ),
  ) %>% 
  arrange(position_location_geo_location_code_n_distinct)

prep_location_n_distinct %>% 
  skim()
```

Aggregate location data to deduplicate, assigning locations by least and most common.

```{r}
prep_location_common <-
  prep_location %>%
  left_join(location_count) %>% 
  group_by(usajobs_control_number
           ,position_close_date, 
           position_open_date
           ) %>%
  arrange(usajobs_control_number
           ,position_close_date, 
           position_open_date,
          rank) %>% 
  summarise(
    across(
      .cols = everything(),
      .fns = list(most_common = first, least_common = last),
      .names = "{.col}_{.fn}"
      )
  ) %>% 
  ungroup()

prep_location_common %>% 
  skim()
```

# CONTINUE FROM HERE

@@

Also create a building dataframe to add other deduplicated dataframes.

```{r}
prep_building <- prep_uniq
```

@@

```{r}
duplicating_variables <- 
  duplicating_variables %>% 
  mutate(group = 
           case_when(variable == "position_open_date" ~ "dates",
                     variable == "position_close_date" ~ "dates",
                     variable == "announcement_closing_type" ~ "announcement_closing_type",
                     variable == "announcement_closing_type_description" ~ "announcement_closing_type",
                     variable == "announcement_closing_type_option" ~ "announcement_closing_type",
                     variable == "application_limit" ~ "application_limit",
                     variable == "application_limit_set" ~ "application_limit",
                     variable == "application_limit_number" ~ "application_limit",
                     variable == "agency_level" ~ "agency_level",
                     variable == "agency_level_sort" ~ "agency_level",
                     variable == "hiring_agency_code" ~ "agency_level",
                     variable == "hiring_agency_name" ~ "agency_level",
                     variable == "hiring_department_code" ~ "agency_level",
                     variable == "hiring_department_name" ~ "agency_level",
                     variable == "maximum_salary" ~ "maximum_salary",
                     variable == "minimum_salary" ~ "maximum_salary",
                     variable == "maximum_grade" ~ "maximum_salary",
                     variable == "minimum_grade" ~ "maximum_salary",
                     variable == "series" ~ "series",
                     variable == "series_title" ~ "series",
                     variable == "mission_critical_code" ~ "mission_critical_code",
                     variable == "mission_critical_code_description" ~ "mission_critical_code",
                     variable == "mission_critical_source" ~ "mission_critical_code",
                     TRUE ~ variable
                     ))

@@

```{r}
duplicating_groups <- 
  duplicating_variables %>% 
  select(group) %>% 
  distinct() %>% 
  arrange(group) %>% 
  pull()

@@

#### Step `r step_n`: `agency_level`

1.    Department of Defense agencies are duplicated because sometimes sub-departments (e.i. Department of Navy) are considered the *Department*
2.    Many duplicates are caused by blank values in hiring agency code and agency level.

First let's remove duplicates because of department. To do this, we will group by control number, then arrange by and control number and descending agency level. Then, we take the data in the first entry.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  group_by_at(params$unique_identifier_1) %>% 
  arrange(usajobs_control_number,desc(agency_level)) %>% 
  summarise(
    across(
      .cols = everything(),
      .fns = first
    )
  ) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

Now we will apply all of these to the whole dataframe.

```{r}
dedupe <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  group_by_at(params$unique_identifier_1) %>% 
  arrange(usajobs_control_number,desc(agency_level)) %>% 
  summarise(
    across(
      .cols = everything(),
      .fns = first
    )
  ) %>% 
  distinct() %>% 
  ungroup()

Let's review this data set.

```{r}
prep_xx <- 
  dedupe

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

#### Step `r step_n`: `announcement_closing_type`

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe. We will update the NA column to include announcements where there are no other indicators equal to one except NA.

```{r}
prep_xx <-
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,announcement_closing_type_description,"closing_type") %>% 
  mutate(
    closing_type_na = case_when(
      closing_type_closing_date == 1 ~ 0,
      closing_type_applicant_cut_off == 1 ~ 0,
      closing_type_open_continuous == 1 ~ 0,
      closing_type_missing == 1 ~ 0,
      closing_type_closing_time == 1 ~ 0,
      closing_type_na == 1 ~ 1,
    )
  )

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

#### Step `r step_n`: `announcement_number`

@@

Apply this to the entire dataframe.

```{r}
dedupe <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  mutate(
    announcement_number = str_to_upper(announcement_number)
  ) %>% 
  distinct() %>% 
  arrange(params$unique_identifier_1,announcement_number) %>% 
  group_by_at(params$unique_identifier_1) %>% 
  summarise(announcement_number = first(announcement_number)) %>% 
  ungroup()

@@

Review the dataframe.

```{r}
prep_xx <- 
  dedupe

@@

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

@@

#### Step `r step_n`: `application_limit`

@@

Not too many. It appears that `application_limit_set` is "N" when `application_limit` is "Applicant Cut-Off". Also `application_limit_number` appears to only be valid when `application_limit_set` is NA.

Now let's look at `application_limit_number`.

```{r}
prep_base %>% 
  filter(!is.na(application_limit_number)) %>% 
  select(all_of(params$unique_identifier_1),application_limit_number) %>% 
  distinct()
```

Only a very few rows have values for `application_limit_number`. We will drop this column.

All NA `application_limit` are "N" `application_limit_set`. Also NA in `application_limit_set` have values in `application_limit`. We will apply the `application_limit` values to NAs in `application_limit_set`.

```{r}
prep_xx <- 
  prep_base %>% 
  mutate(
    application_limit_set = case_when(is.na(application_limit_set) ~ application_limit,
                                      TRUE ~ application_limit_set)
  ) %>% 
  character_to_indicator(params$unique_identifier_1,application_limit_set,"application_limit_set") %>% 
  # Drop the "N" column
  select(-application_limit_set_n)

@@

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

@@

#### Step `r step_n`: `appointment_type``

@@

Lots of them, but appears to be mainly because of NAs.

We'll want to transform these into indicators and transform the NAs so that they are only for *true* NAs.

@@

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,appointment_type,"appointment_type") %>% 
  mutate(
    appointment_type_na = case_when(
      appointment_type_permanent == 1 ~ 0,
      appointment_type_term == 1 ~ 0,
      appointment_type_intermittent == 1 ~ 0,
      appointment_type_temporary == 1 ~ 0,
      appointment_type_internships == 1 ~ 0,
      appointment_type_multiple_appointment_types == 1 ~ 0,
      appointment_type_temporary_promotion == 1 ~ 0,
      appointment_type_recent_graduates == 1 ~ 0,
      appointment_type_detail == 1 ~ 0,
      appointment_type_seasonal == 1 ~ 0,
      appointment_type_agency_employees_only == 1 ~ 0,
      appointment_type_summer == 1 ~ 0,
      appointment_type_ictap_only == 1 ~ 0,
      appointment_type_presidential_management_fellows == 1 ~ 0,
      appointment_type_telework == 1 ~ 0,
      appointment_type_na == 1 ~ 1
    )
  )

@@

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

@@

#### Step `r step_n`: `dates`

@@

Duplication appear to be because of difference in open and close dates. After messaging with Melissa, we decide to retain the dates as determined by the close date.

@@

```{r}
prep_xx <- 
  prep_base %>% 
   select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

@@

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

@@

#### Step `r step_n`: `disable_apply_online`

@@

Quite a few. It appears that `disable_apply_online` in NA in many duplicates.

@@

@@

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,disable_apply_online,"disable_apply_online") %>% 
  mutate(
    disable_apply_online_na = case_when(
      disable_apply_online_n == 1 ~ 0,
      disable_apply_online_y == 1 ~ 0,
      disable_apply_online_na == 1 ~ 1
    )
  )

@@

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

@@

#### Step `r step_n`: `hiring_subelement_name`

@@

#### Step `r step_n`: `is_remote_work_eligible`

```{r}
prep_xx <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  mutate(
    is_remote_work_eligible = case_when(is_remote_work_eligible == "" ~ "N",
                                        is_remote_work_eligible == "NULL" ~ "N",
                                        TRUE ~ is_remote_work_eligible)
  ) %>% 
  distinct() %>% 
  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
                         in_variable = is_remote_work_eligible,
                         in_prefix = "is_remote_work_eligible") %>% 
  # Drop the "n" indicatoris_remote_work_eligible
  select(-is_remote_work_eligible_n)

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

#### Step `r step_n`: `maximum_salary`

@@

```{r}
prep_xx <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

@@

Join to building dataframe.

```{r}
prep_building <- prep_building %>% 
  left_join(prep_xx)
```

@@

#### Step `r step_n`: `mission_critical_code`

@@

Let's count the entries here.

```{r}
prep_base %>% 
  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
  count()
```

Lots of entries here. So we don't want to make indicators. Looks like they are created by rows with a null. We'll count how many nulls and entries with values.

```{r}
dupe_02 %>% 
  mutate(cause = case_when(is.na(mission_critical_code) ~ 'null',
                           TRUE ~ 'value'),
         ind = 1) %>% 
  select(usajobs_control_number,cause,ind) %>% 
  distinct() %>% 
  pivot_wider(names_from = cause, values_from = ind) %>% 
  summarise(
    unique = n_distinct(usajobs_control_number),
    nulls = sum(null),
    values = sum(value, na.rm = TRUE)
  )
```

Select the rows that have an entry if they have that.

```{r}
prep_xx <- 
  prep_base %>% 
    select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>%
  arrange(usajobs_control_number,mission_critical_code) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .fns = first
    )
  ) %>% 
  ungroup()

@@

#### Step `r step_n`: `number_of_views`

@@

Let's count the entries here.

```{r}
prep_base %>% 
  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
  count()
```

This looks pretty unreliable. We dill drop `number_of_views`.

#### Step `r step_n`: `position_opening_status`

Let's count the entries.

```{r}
prep_base %>% 
  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
  count()
```

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe. We will update the NA column to include announcements where there are no other indicators equal to one except NA.
